### 2016-07-05 introduction.tex
edits

In this paper, we propose a program logic for weakly-isolated
transactions that realizes this goal.  In particular, we develop a set
of syntax-directed compositional proof rules that allow developers to
build correctness proofs for transactional programs in the presence of
a weakly-isolated concurrency control mechanism.  A key novelty of our
approach is that it is parametric over the \emph{isolation semantics}
of transactions in the program, as well as the \emph{consistency
  semantics} of the underlying store. In concrete terms, this means
that, unlike recent work focused on formalizing the semantics of weak
consistency~\cite{gotsmanpopl16, redblueatc, ecinec}, our system model
does not assume a minimum or predefined set of consistency or
isolation levels. Instead, our operational semantics admits
declarative specifications of transaction isolation and store
consistency levels (\eg~\cite{pldi15,gotsmanconcur15}), and generates
executions that are guaranteed to satisfy these specifications. The
result is a flexible system model that is general enough to
incorporate the semantics of a range of isolation levels on a variety
of stores (\eg the sequentially consistent store of~\cite{adyaphd}, or
the causally consistent store of~\cite{gotsmanpopl16}, etc).  Our key
technical contribution is thus a set of proof rules that demonstrate
that a program with a given selection of isolation levels for its
transactions preserves its invariants when executed on a store
equipped with certain consistency guarantees (e.g., causal
visibility).

The paper makes the following contributions:
\begin{itemize}
  \item We develop a semantics for a core language equipped with
    weakly-isolated transactions, demonstrating that a general
    parametric isolation semantics can be expressed as
    well-formedness constraints on a program's execution.
  \item We present a compositional proof system for this language
    capable of relating high-level application invariants to the structure
    of traces induced by the operational semantics, in which transactions
    are associated with specific weak isolation levels.
  \item We define a \emph{maximum visibility principle} to reconcile
    store consistency guarantees with transaction isolation
    requirements, and use it to instantiate our operational model and
    the proof system for various kinds of (weakly-consistent) data
    stores.
  \item Case studies modeled after real-world scenarios demonstrate
    the applicability and utility of our proof methodology.
\end{itemize}

>>>>

In this paper, we propose a program logic for weakly-isolated
transactions that realizes this goal.  In particular, we develop a set
of syntax-directed compositional proof rules that allow developers to
build correctness proofs for transactional programs in the presence of
a weakly-isolated concurrency control mechanism.  A key novelty of our
approach is that it is parametric over the \emph{isolation semantics}
of transactions in the program, as well as the \emph{consistency
  semantics} of the underlying store. In concrete terms, this means
that, unlike recent work focused on formalizing the semantics of weak
consistency~\cite{gotsmanpopl16, redblueatc, ecinec}, our system model
does not assume a minimum or predefined set of consistency or
isolation levels. Instead, our operational semantics admits
declarative specifications of transaction isolation and store
consistency levels (\eg~\cite{pldi15,gotsmanconcur15}), and generates
executions that are guaranteed to satisfy these specifications. The
result is a flexible system model that is general enough to
incorporate the semantics of a range of isolation levels on a variety
of stores (\eg the sequentially consistent store of~\cite{adyaphd}, or
the causally consistent store of~\cite{gotsmanpopl16}, etc).  Our key
technical contribution is thus a set of proof rules that demonstrate
that a program with a given selection of isolation levels for its
transactions preserves its invariants when executed on a store
equipped with appropriate consistency guarantees  (\emph{e.g.}, causal
visibility).

The paper makes the following contributions:

\begin{itemize}
  \item We develop a semantics for a core language equipped with
    weakly-isolated transactions, demonstrating that a general
    parametric isolation semantics can be expressed as
    well-formedness constraints on a program's execution.
  \item We present a compositional proof system for this language
    capable of relating high-level application invariants to the structure
    of traces induced by the operational semantics, in which transactions
    are associated with specific weak isolation levels.
  \item We define a \emph{maximum visibility principle} to reconcile
    store consistency guarantees with transaction isolation
    requirements, and use it to instantiate our operational model and
    the proof system for various kinds of (weakly-consistent) data
    stores.
  \item Case studies modeled after real-world scenarios demonstrate
    the applicability and utility of our proof methodology.
\end{itemize}
